---
title: "Global Down Syndrome Organization Clinic List"
author: "M. E. Waggoner"
date: "June 20, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(rvest)
require(tidyverse)
```

##  Scraping the data



Get a list of states that have clinics.  At first I thought this would be needed to read the websites, but it turns out that I needed for information for each clinic for states with more than one clinic.

```{r}

root_url <- "https://www.globaldownsyndrome.org/research-medical-care/medical-care-providers/"
  
GlobalDSFdn <- 
  read_html(root_url)


GlobalDSFdn %>% 
  html_nodes("#map a") %>% 
  html_text() %>% 
  str_to_lower() ->
  States

States

```

```{r}



# Create a list of state names and nodes.  
# There will be one row for each clinic.  
# Selector Gadget was used to obtain the nodes.
state_and_node = tibble( state = character(),
                         node = character())

state_and_node %>% 
  add_row( state = "iowa", node = "td , #cdd h2") %>% 
  add_row( state = "colorado", node = "td" ) %>%
  add_row( state = "delaware", node = "td" ) %>%
  add_row( state = "louisiana", node = "td" ) %>%
  add_row( state = "minnesota", node = "td" ) %>%
  add_row( state = "montana", node = "td" ) %>%
  add_row( state = "north dakota", node = "td" ) %>%
  add_row( state = "oregon", node = "td" ) %>%
  add_row( state = "south dakota", node = "#sanford :nth-child(1)" ) %>%  
  # add_row( state = "tennessee", node = "td" ) %>%
  # # add_row( state = "virginia", node = "td" ) %>%  
  # add_row( state = "washington", node = "td" ) %>%
  # add_row( state = "massachusetts", node = "table:nth-child(12) td") %>% 
  # add_row( state = "massachusetts", node = "table:nth-child(9) td , table:nth-child(9) h2") %>% 
  add_row( state = "arizona", node = "td")   ->
    state_and_node

# Create a blank tibble for the Clinic data
# the other variable names will be created on the fly
Clinics <- tibble(state = character(),
                  name = character()     )

# For each clinic (i), parse the information from the html
# and place in the Clinics tibble.
for (i in 1:nrow(state_and_node)) {


  # create the clinich URL by appending the state 
  # and a backslash to the root URL
  clinic_url <- paste(root_url, 
                      state_and_node[i, "state"],
                      "/", 
                      sep = "")
  
  # read the clinic site html then save the html
  # (as text) and then parse it using html_text()
  clinic_site <- read_html(clinic_url)

  clinic_site %>% 
    html_nodes(as.character(state_and_node[i, "node"]))->
    clinic_html
  
  clinic_html %>% 
    html_text() %>% 
    str_replace_all("[\r\n]" , "") ->
    clinic_text
  
  # Start populating the Clinic tibble
  # all clinics have a state and a name
  
  Clinics[i,"state"] <- 
    string_to_title(state_and_node[i, "state"])
  Clinics[i,"name"] <- clinic_text[1]
  
  # loop through each line of the html text pulling out
  # variable data and storing it in Clinics tibble
  for(n in 2:length(clinic_text)) {
  
    # n_service is a flag that there was a services form
    # to read from - initially set to FALSE
    n_service <- FALSE
  
    # grab the position of a final ":" or "?"
    # these indicate a variable title and the data following
    # in the next line is the data for that variable
    pos <- str_locate(clinic_text[n], ":$")[1]
    if (is.na(pos)) {
      pos <- str_locate(clinic_text[n], "\\?$")[1]
      }
    
    # if there was a final ":" or "?"
    # create the variable name (var_name) from the text
    # preceding the punctuation and remove all spaces
    # If the variable name is "Servicesprovided" set the
    # n_service flag to TRUE so we can parse the services
    if (!is.na(pos) ) {
      var_name <- clinic_text[n] %>% 
        str_sub(1, pos - 1) %>% 
        str_replace_all(" " , "")
      Clinics[i, var_name] <- clinic_text[n + 1]
      if (var_name == "Servicesprovided") {
        n_service <- TRUE
      }
    }
  }
  
  # If there was a ServicesProvided form, then
  # parse the three columns
  
  if(n_service) {
    
    # create a blank location tibble for each clinic
    # we will store the parsed information there
    location <- tibble(start = numeric(), 
                       end = numeric(),
                       text = character(),
                       checked = logical())
    
    # loop through each column 
    for (m in 1:3) {
      
      #create a node name for each column
      # read the HTML for that node
      # convert to text and split at the beginning of 
      # each tag - some of these tags are checkboxes
      node <- paste("td:nth-child(",
                    as.character(m),
                    ") form", 
                    sep = "")
      clinic_site %>% 
        html_node(node)  -> form
      as.character(form) -> mytext
      str_split(mytext, "<") -> mytext2
      
      # loop through each line we split out from the 
      # HTLM code
      strs <- length(mytext2[[1]])
      for (k in 1:strs){
        
        # look for end of the tag (> character)
        # the service provided will follow the tag end
        # save the start and end indices in the location
        # tibble - making sure to allow for the 2nd
        # and 3rd columns (k + (m - 1)*strs)
        tag_end <- str_locate(mytext2[[1]][k], "[^>]*$")
        location[k + (m-1)*strs, 1] <- tag_end[1]
        location[k + (m-1)*strs, 2] <- tag_end[2]
        
        
        # if the end location is greater than the 
        # start location, this means there was a tag 
        # on that line
        if (location[k + (m-1)*strs, 1] < 
            location[k + (m-1)*strs,2]) {
          
          # If there was a tag, then extract the
          # variable name from the end of the line
          # after the tag end, remove spaces and slashes
          location[k + (m-1)*strs, 3] <- 
            str_extract(mytext2[[1]][k], "[^>]*$") %>% 
            str_replace_all(" " , "") %>% 
            str_replace_all("/" , "")
        
          # check to see if there is the word "true"" or    
          #  "checked" on the line.  If so
          # then the service is offered
          location[k + (m-1)*strs, 4] <- FALSE
          log_loc <- str_locate(mytext2[[1]][k], "true")
          if (is.na(log_loc[1]) ) {
            log_loc <- 
              str_locate(mytext2[[1]][k], "checked")
          }
          if (!is.na(log_loc[1]) && 
              log_loc[1] < log_loc[2]) {
            location[k + (m-1)*strs, 4] <- TRUE
          }
        } 
      }
    }
    location %>% 
      filter(!is.na(text)) -> location
    for (j in 1:nrow(location)) {
      var_name <- as.character(location[j, 3])
      Clinics[i, var_name] <- location[j, 4]
    }
  
   }
}
Clinics 



```
## Issues

* Need the nodes for the rest of the clinics.

    * It appears that "td" will work for states with only 1 clinic.
    
* The group made some phone calls and need to incorporate the information they have from there.
